A Spiking Independent Accumulator Model for Winner-Take-All

### 2017-01-22 doc/paper/paper.tex
Intro iteration / fixup

The winner-take-all (WTA) mechanism is a component that selects the largest value among a number of possible inputs.
More specifically, the input is a $d$-dimensional vector corresponding to the non-negative utility of $d$ different choices, and the desired output is positive for the dimension with highest utility (i.e., the ``winner'') and zero for all others.
This mechanism is regularly employed in cognitive models of decision making, which must select the most important action to take at any given moment in time~\cite<e.g.,>{oreilly1998}. 
\todo{Cite survey or cite other examples}

>>>>

The winner-take-all (WTA) mechanism is a network that selects the largest value among a number of possible inputs.
More precisely, given a $d$-dimensional vector corresponding to the non-negative utility of $d$ different choices, the desired output is positive for the dimension with highest utility (i.e., the ``winner'') and zero for all others.
This mechanism is regularly employed as a component of cognitive models involving decision making, in which the most useful action is selected to drive behaviour~\cite<e.g.,>{oreilly1998}. 
\todo{Cite survey or cite other examples}
